An Algorithmic Introduction to Lagrangian Coherent Structures

### 2013-11-11 main.tex
Change ocean data-set demo from backward time strainlines to forward time stretchlines.

The forward time LCS obtained are shown in Figure~\ref{f:double gyre hyperbolic shear lcs forward} and the backward time LCS (i.e. with the flow timespan set to $t \in [20,0]$) are shown in Figure~\ref{f:double gyre hyperbolic shear lcs backward}. In Figures~\ref{f:double gyre hyperbolic shear lcs details forward} and~\ref{f:double gyre hyperbolic shear lcs details backward} the same LCS are shown with details: the finite-time Lyapunov exponent, closed shearlines inside the outermost shearlines and $\lambda_2$ local maximums used for strainline integration initial positions.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/double_gyre/hyperbolic_shear_lcs_details_strainline}
\end{center}
\caption{Same LCS as in Figure~\ref{f:double gyre hyperbolic shear lcs strainline}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed lambda-lines with thick green curves being outermost closed lambda-lines, i.e. lambda-line LCSs. White dots indicate $\lambda_2$ local maximums used for strainline integration initial positions.}
\label{f:double gyre hyperbolic shear lcs details forward}
\end{figure}

\begin{figure}
\begin{center}
% LCS Tool commit ac3a7705aec81577b1aba3cafe598066dd689203
\includegraphics[width=\textwidth]{graphics/double_gyre/hyperbolic_shear_lcs_details_stretchline}
\end{center}
\caption{Same LCS as in Figure~\ref{f:double gyre hyperbolic shear lcs stretchline}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed lambda-lines and thick green curves are outermost lambda-lines, i.e. lambda-line LCSs. White dots indicate $\lambda_1$ local minimums used for stretchline integration intial positions.}
\label{f:double gyre hyperbolic shear lcs details stretchline}
\end{figure}

@@

The forward time LCS obtained are shown in Figure~\ref{f:bickley jet hyperbolic shear lcs strainline} and the backward time LCS (i.e. with the flow timespan set to $t \in [4 L_x/U,0]$ are shown in Figure~\ref{f:bickley jet hyperbolic shear lcs stretchline}. In Figures~\ref{f:bickley jet hyperbolic shear lcs details forward} and~\ref{f:bickley jet hyperbolic shear lcs details backward} the same LCS are shown with details.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/bickley_jet/hyperbolic_shear_lcs_details_strainline}
\end{center}
\caption{Same LCS as in Figure~\ref{f:bickley jet hyperbolic shear lcs forward}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed shearlines with thick green curves are outermost shearlines, i.e. shear LCS. White dots indicate $\lambda_2$ local maximums used for strainline integration initial positions.}
\label{f:bickley jet hyperbolic shear lcs details forward}
\end{figure}

\begin{figure}
\begin{center}
% demo/bickley_jet/hyperbolic_shear_lcs_details.m, commit 3331187
\includegraphics[width=\textwidth]{graphics/bickley_jet/hyperbolic_shear_lcs_details_stretchline}
\end{center}
\caption{Same LCS as in Figure~\ref{f:bickley jet hyperbolic shear lcs backward}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed shearlines with thick green curves are outermost shearlines, i.e. shear LCS. White dots indicate $\lambda_2$ local maximums used for strainline integration initial positions.}
\label{f:bickley jet hyperbolic shear lcs details backward}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/ocean_dataset/hyperbolic_shear_lcs_strainline}
\end{center}
\caption{Ocean dataset forward time shear (green) and hyperbolic (red) LCS.}
\label{f:ocean dataset hyperbolic shear lcs strainline}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/ocean_dataset/hyperbolic_shear_lcs_stretchline}
\end{center}
\caption{Ocean dataset backward time shear (green) and hyperbolic (blue) LCS.}
\label{f:ocean dataset hyperbolic shear lcs stretchline}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/ocean_dataset/hyperbolic_shear_lcs_details_strainline}
\end{center}
\caption{Same LCS as in Figure~\ref{f:ocean dataset hyperbolic shear lcs forward}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed shearlines with thick green curves are outermost shearlines, i.e. shear LCS. White dots indicate $\lambda_2$ local maximums used for strainline integration initial positions.}
\label{f:ocean dataset hyperbolic shear lcs details forward}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/ocean_dataset/hyperbolic_shear_lcs_details_stretchline}
\end{center}
\caption{Same LCS as in Figure~\ref{f:ocean dataset hyperbolic shear lcs backward}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed shearlines with thick green curves are outermost shearlines, i.e. shear LCS. White dots indicate $\lambda_2$ local maximums used for strainline integration initial positions.}
\label{f:ocean dataset hyperbolic shear lcs details backward}
\end{figure}

>>>>

The forward time LCS obtained are shown in Figure~\ref{f:double gyre hyperbolic shear lcs strainline} and the backward time LCS (i.e. with the flow timespan set to $t \in [20,0]$) are shown in Figure~\ref{f:double gyre hyperbolic shear lcs stretchline}. In Figures~\ref{f:double gyre hyperbolic shear lcs details strainline} and~\ref{f:double gyre hyperbolic shear lcs details stretchline} the same LCS are shown with details: the finite-time Lyapunov exponent, closed shearlines inside the outermost shearlines and $\lambda_2$ local maximums used for strainline integration initial positions.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/double_gyre/hyperbolic_shear_lcs_details_strainline}
\end{center}
\caption{Same LCS as in Figure~\ref{f:double gyre hyperbolic shear lcs strainline}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed lambda-lines with thick green curves being outermost closed lambda-lines, i.e. lambda-line LCSs. White dots indicate $\lambda_2$ local maximums used for strainline integration initial positions.}
\label{f:double gyre hyperbolic shear lcs details strainline}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/double_gyre/hyperbolic_shear_lcs_details_stretchline}
\end{center}
\caption{Same LCS as in Figure~\ref{f:double gyre hyperbolic shear lcs stretchline}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed lambda-lines and thick green curves are outermost closed lambda-lines, i.e. lambda-line LCSs. White dots indicate $\lambda_1$ local minimums used for stretchline integration intial positions.}
\label{f:double gyre hyperbolic shear lcs details stretchline}
\end{figure}

@@

The forward time LCS obtained are shown in Figure~\ref{f:bickley jet hyperbolic shear lcs strainline} and the backward time LCS (i.e. with the flow timespan set to $t \in [4 L_x/U,0]$ are shown in Figure~\ref{f:bickley jet hyperbolic shear lcs stretchline}. In Figures~\ref{f:bickley jet hyperbolic shear lcs details strainline} and~\ref{f:bickley jet hyperbolic shear lcs details stretchline} the same LCS are shown with details.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/bickley_jet/hyperbolic_shear_lcs_details_strainline}
\end{center}
\caption{Same LCS as in Figure~\ref{f:bickley jet hyperbolic shear lcs strainline}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed lambda-lines with thick green curves being outermost closed lambda-lines, i.e. lambda-line LCSs. White dots indicate $\lambda_2$ local maximums used for strainline integration initial positions.}
\label{f:bickley jet hyperbolic shear lcs details strainline}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/bickley_jet/hyperbolic_shear_lcs_details_stretchline}
\end{center}
\caption{Same LCS as in Figure~\ref{f:bickley jet hyperbolic shear lcs stretchline}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed lambda-lines with thick green curves being outermost closed lambda-lines, i.e. lambda-line LCSs. White dots indicate $\lambda_2$ local maximums used for stretchline integration initial positions.}
\label{f:bickley jet hyperbolic shear lcs details stretchline}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/ocean_dataset/hyperbolic_shear_lcs_strainline}
\end{center}
\caption{Ocean dataset lambda-line (green) and strainline (red) LCS.}
\label{f:ocean dataset hyperbolic shear lcs strainline}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/ocean_dataset/hyperbolic_shear_lcs_stretchline}
\end{center}
\caption{Ocean dataset lambda-line (green) and stretchline (blue) LCSs.}
\label{f:ocean dataset hyperbolic shear lcs stretchline}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/ocean_dataset/hyperbolic_shear_lcs_details_strainline}
\end{center}
\caption{Same LCS as in Figure~\ref{f:ocean dataset hyperbolic shear lcs strainline}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed lambda-lines with thick green curves being outermost closed lambda-lines, i.e. lambda-line LCSs. White dots indicate $\lambda_2$ local maximums used for strainline integration initial positions.}
\label{f:ocean dataset hyperbolic shear lcs details strainline}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/ocean_dataset/hyperbolic_shear_lcs_details_stretchline}
\end{center}
\caption{Same LCS as in Figure~\ref{f:ocean dataset hyperbolic shear lcs stretchline}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed lambda-lines and thick green curves are outermost closed lambda-lines, i.e. lambda-line LCSs. White dots indicate $\lambda_1$ local minimums used for stretchline integration intial positions.}
\label{f:ocean dataset hyperbolic shear lcs details stretchline}
\end{figure}
